Towards a Machine Learning approach for Aggregate Computing

### 2021-11-28 paper-2021-woa-ac-ml.tex
Citation needed if we claim AC to be used in various apps

AC is studied in various simulated scenarios ranging from smart cities to crowds, 
 thanks to Alchemist~\cite{DBLP:journals/jos/PianiniMV13} (a meta-simulator for pervasive systems) and to programming languages and toolchains that support 
 this paradigm, such as ScaFi~\cite{DBLP:conf/isola/CasadeiVAD20}. %, FCCP~\cite{DBLP:conf/acsos/Audrito20} and Protelis~\cite{PianiniSAC2015}.

>>>>

AC is studied in various simulated scenarios ranging from smart cities to crowd management~\cite{DBLP:journals/jlap/ViroliBDACP19}, 
 thanks to Alchemist~\cite{DBLP:journals/jos/PianiniMV13} (a meta-simulator for pervasive systems) and to programming languages and toolchains that support 
 this paradigm, such as ScaFi~\cite{DBLP:conf/isola/CasadeiVAD20}. %, FCCP~\cite{DBLP:conf/acsos/Audrito20} and Protelis~\cite{PianiniSAC2015}.
